CS378: Final Project - Data Artifacts \\ \url{https://github.com/sarimaleem/cs378_fp}

### 2023-04-27 paper/main.tex
checkpoint

In order to test if the model is finding artifacts in the data or genuinely
evaluating it, we annotated 50 different examples in the validation data that
the model predicted correctly, and then tested to see if the model was able to
predict them correctly again.

\subsection{Using contast sets to evaluate the model}

\todo{Describe clearly how you conducted your analysis of the model
performance, and report the outcomes. You should provide (1) some examples of
both \textbf{specific errors/behavior} from the model and (2) analysis or
discussion of \textbf{the general class of mistakes the model makes}. For
characterizing the general class, try to come up with rules that can identify
a set of challenging examples (e.g., ``examples containing \emph{not}'') and
try to visualize in charts, graphs, or tables what you believe to be relevant
statistics about the data. For example, how frequent is the class of examples
where such error pattern apply? This part of the report should be at least one
page.}

% Describe clearly how you conducted your analysis of the model
% performance, and report the outcomes. You should provide (1) some examples of
% both \textbf{specific errors/behavior} from the model and (2) analysis or
% discussion of \textbf{the general class of mistakes the model makes}. For
% characterizing the general class, try to come up with rules that can identify a
% set of challenging examples (e.g., ``examples containing \emph{not}'') and try
% to visualize in charts, graphs, or tables what you believe to be relevant
% statistics about the data. For example, how frequent is the class of examples
% where such error pattern apply? This part of the report should be at least one
% page.

@@

% You should describe modifications you have made to improve performances.
% We will evaluate based on how reasonable is your fix  -- if your fix and
% motivation does not link, your modificiation is unreasonable. For example,
% perhaps you tried to modify neural network training in a way that is totally
% unconnected to your stated goal, or your modification was erroneous. Describe
% the baseline model to be compared to your approach as well here. Again, clearly
% define all notations. Someone who is reading your report (with reasonable
% background, e.g., your classmates in this course) should have a reasonable idea
% how to implement it themselves. Describe hyperparameters, including how they
% are selected, if you have hyperparameters involved.

>>>>

In order to test if the model is finding artifacts in the data or genuinely
evaluating it, we annotated 35 different examples in the validation data that
the model predicted correctly, and then tested to see if the model was able to
predict them correctly again.

The results of the model showed a significant dip in accuracy, with accuracy
going down to 77\% from 89\%. The model mispredicted 8/35 examples. One pattern
that emerged from the mispredictions is that the model fails to see correlations
between various words and also fails to understand the relationships between
various words. The following is an example of this phenomenon: \\

\begin{quote}
premise: Two men on vehicles competing in a race. \\
hypothesis: Men are riding cars on the street. \\
label: neutral \\
predicted: contradiction
\end{quote}

The neural network is essentially unable to distinguish that different words can
have the same meaning (in this case vehicles and cars).

@@
